Trends of downward SDR in Thessaloniki

### 2023-04-27 Article.Rmd
Commit 2023-04-27 20:17

---
title:         "Trends of downward SDR in Thessaloniki "
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions."

@@

```{r echo=F, include=F, cache=T}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
# knitr::opts_chunk$set(dev        = "png"    )
knitr::opts_chunk$set(out.width  = "80%"   )
knitr::opts_chunk$set(fig.align  = "center" )
knitr::opts_chunk$set(fig.pos    = '!h'    )

@@

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the the Suns intensity variability, using an homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->

@@

In this study, we present any radiometric data as an percent departure from the corresponding seasonal mean.
When we use daily aggregated data we compute the mean values for the day and exclude instances with less than `r  Daily_aggregation_N_lim` valid data points.
Accordingly, monthly values are computed from the daily aggregated data, month with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values are computed based on the day of year number and the monthly by the calendar month.

@@

@@

\tiny 
```{r echo=F}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp,
               caption = "Table of trends and stats")
```
\normalsize

>>>>

---
title:         "Trends of downward SDR in Thessaloniki"
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisphysicist@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions."

@@

```{r echo=F, include=F, cache=T}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = '!h'    )

@@

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all 1-minute radiometric values to the mean Sun - Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the Suns intensity variability, using a homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->

@@

In this study, we present any radiometric data as a percent departure from the corresponding seasonal mean.
When we use daily aggregated data we compute the mean values for the day and exclude instances with less than `r Daily_aggregation_N_lim` valid data points.
Accordingly, monthly values are computed from the daily aggregated data, month with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values are computed based on the day of year number and the monthly by the calendar month.

@@

## Long term trends by season of year

```{r seasonalALL, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/SeasonaltTrends-1.pdf")
```

```{r seasonalCLEAR, echo=F, fig.cap="Daiditions."}
knitr::include_graphics("./images/SeasonaltTrends-2.pdf")
```

```{r seasonalCLOUD, echo=F, fig.cap="Daiditions."}
knitr::include_graphics("./images/SeasonaltTrends-3.pdf")
```

@@

<!--\tiny -->
```{r echo=F}
pp <- data.table::fread("./figures/tbl_longterm_trends.dat")
pander::pander(pp,
               caption = "Table of trends and stats")
```
<!--\normalsize-->
